\LARGE \bf Budgeted Multi-Armed Bandit Models for Sample-Based Grasp Planning in the Presence of Uncertainty

### 2014-12-19 paper.tex
changed structure, pushed GPIS stuff to appendix, changed story to be sampled from graphical model

\author{Michael Laskey$^1$, Zoe McCarthy$^1$, Jeff Mahler$^1$, Florian T. Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\small \{fpokorny, dani\}@kth.se}}%
\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\small jurvandenberg@gmail.com}}%
}

@@

Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and even material properties like friction coefficient or center of mass.  Due to sensor noise and missing data due to partial visibility and object properties such as transparency, the robot may not be able to measure these quantities exactly.
Grasp planners that assume prior knowledge of object geometry or an exact measurement of pose may fail in this environment.

Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaulate a grasp assuming all the parameters are known \cite{ferrari1992}.
This motivates using knowledge of uncertainty to select grasps, but most methods for evaluating the quality of a single grasp in the presence of uncertainty require use of an exhaustive sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
To select a grasp with high quality this evaluation is often performed for a large set of potential grasps, which can be very time-consuming.
However, when evaluating a set of grasps we may be able to determine the difference of quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
Thus, we can adaptively concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.

@@

Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a budgeted multi-armed bandit model.
We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality \cite{ferrari1992} under shape uncertainty.
We use a budgeted multi-armed bandit model since we would like to execute only one grasp plan after evaluating the expected quality of many potential grasp plans.
We choose the model of uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013}, however the method applies to any model of uncertainty that can be sampled.
We also show how to estimate distributions on the contact points and surface normals and center of mass using a GPIS shape representation. We then leverage these distributions to reduce the computational complexity of sampling from the GPIS model from $O(n^6)$ to $O(n^3)$, where the workspace is discretized as a $n \times n$ grid. Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x, an order of magnitude improvement, over the baseline Monte-Carlo approach. These promising results suggest that our MAB approach could be used on other types of uncertainty, such as pose, friction coefficent or center of mass and provide significant speed improvements.

@@

Currently, the most common method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.
To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps. The adaptive sampling pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is. 
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution~\cite{andrieu2003introduction}.

@@

There are a number of algorithms for developing policies to balance exploration and exploitation.
One algorithm is $\epsilon-$greedy, which is the idea of choosing the arm with the highest empirical expected reward with $1-\epsilon$ probability and choosing a random arm with probability $\epsilon$ \cite{barto1998reinforcement}.
A class of algorithms that have stronger theoretical guarantees are from the Upper Confidence Bound (UCB) family.
UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times each arm has been sampled. 
Traditional bandit algorithms minimize cumulative regret, which is the sum over each sub-optimal arm of the number of times that arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm.
%In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.

Different to the normal bandit problem, we do not actually care about cumulative regret because the exploration and exploitation stage is decoupled from each other. For example in medical testing for patients it is important to always administer the best treatment for the given patient. However for the case of product testing in cosmetics it does not matter what products are administer in the testing phase, but only what final product is sold to the consumer.

Best arm identification has a wide variety of literature that largely falls into two camps. One where the algorithm terminates once a fixed confidence interval around the best arm is met and one where a set horizon is given and the algorithm has to choose a arm at that stopping time.

\subsection{Fixed Confidence}
In the fixed confidence setting the forecaster seeks to minimize the simple regret until a fixed confidence threshold is met at which point it terminates. Originally the problem was solved by racing algorithms, were methods used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were deemed not likely to succeed and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}. These methods were later extended to include not only the best arm, but return the top m arms \cite{gabillon2012best}.

\subsection{Fixed Budget}
In the fixed budget setting the algorithm is given a stopping time and needs to return the best arm at that stopping time. Audibert el al. demonstrated an algorithm called Successive Rejects that given a budget divides up the time each arm is pull an can return the best arm with near optimal probability depending on the hardness of the problem \cite{audibert2010best}. Other UCB like methods have been proposed as well that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}. In \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed
for the analysis of the existing bandit algorithms like UCB1.

@@

@@

The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m$, surface normals $\textbf{n}_1,...,\textbf{n}_m$, center of mass $z$ and friction coefficient $\mu$. Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. A wrench is defined as concatenation of a force and torque vector.  If the convex hull does not enclose the origin, the grasp is not in force-closure. Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$, our method is applicable to all grasp metrics that represent a grasp as the tuple $g$, such as \cite{christopoulos2007handling}, \cite{li1988task}.

Since we are in an uncertain environment, we are interested in calculating the expected quality, or $P(Q>0)$, or the probability of achieving force closure, similar too  \cite{christopoulos2007handling}\cite{kehoe2012toward} . $P(Q>0)$ is computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed. Reducing the time to find the best expected grasp from a set of a large number of grasps is the primary focus of the paper.

\subsection{Types of Uncertainty}
In this work we consider the following types of uncertainty shape, pose, center of mass and friction coefficient. The probabilistic relationship of all these types of uncertainty can be seen in Fig. \ref{fig:graphical_model}. We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty.

For shape, we use a GPIS representation as described in Sec. \ref{sec:GP}. For pose we sample the centroid of the GPIS from a Gaussian distribution with user covariance matrix. Center of mass a Gaussian  with mean as the expected center of mass, as defined in Eq. \ref{eq:mass}, assuming uniform mass distribution. Lastly, for friction coefficient we represent it as Gaussian with mean around the expected friction coefficient provided by a user.

@@

\subsection{Line of action}
In an uncertain environment one would not actually know the true $g$, thus we have to work with the trajectory of the gripper. Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.

@@

While we currently assume the gripper moves free of noise, this approach would be applicable to high precision robots such as industrial robots. 
Future work will look at how to efficiently sample when the approach trajectory has noise.

@@

Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model, which we describe in Section \ref{sec:GP} and set of possible grasp plans $G$.
We are interested in determining

\begin{align}\label{eq:problem_def}
\Gamma^* \in \mbox{argmax}_{\Gamma \in G} P(Q(\Gamma)>0)
\end{align}

with respect to a chosen grasp metric Q.

\section{Multi-Armed Bandits for Grasp Selection}
While a standard approach to solving the problem in Eq. \ref{eq:problem_def} would be to perform Monte-Carlo integration on each $\Gamma_i$ and compute the expected grasp quality, we propose treating the problem as a multi-armed bandit model and forming a policy for selecting which grasp to sample. 
In our setting, we have a probabilistic shape representation and would like to evaluate many potential grasps on that shape model.
Motivated by limited computational resources we are interested in how to intelligently allocate sampling resources to efficiently find the best grasp plan $\Gamma^*$.
Here each arm corresponds to a different grasp plan and pulling the arm is sampling the shape representation and evaluating the arm's grasp plan on the sampled shape representation.
The reward for pulling an arm is the grasp quality of the resulting grasp on the sampled shape.
We have a policy for exploration of different grasp plans (i.e. choosing which one to sample next) and at a given stopping time we choose to execute the grasp plan with the highest expected quality based on the samples received so far, which would correspond to actually performing the grasp.  
The number of samples needed before the simple regret reaches zero, determines how effective an exploration policy is for grasp evaluation.

In solving Eq. \ref{eq:problem_def}, we want to pick the grasp plan with the highest $P(Q(\Gamma)>0)$ determined via Monte-Carlo Integration.
Since the function to test force closure is boolean, we can model our problem as choosing the best arm for a Beta-Bernoulli Process. Methods with very strong guarantees are now available to us \cite{review}. We now review some of them.
\section{Bandit Algorithms For Best Arm Identification}
\subsection{Thompson Sampling}
Thompson Sampling is a Bayesian method for the multi-armed bandit problem. The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled. Then sample from the prior distribution on all arms and pull the arm with the highest sample drawn. The full algorithm is shown in Algorithm 1.  Empirically this method has been shown to outperform frequentist methods like UCB \cite{chapelle2011empirical}

\subsection{Upper Confidence Bound (UCB)}
The UCB strategy was the first strategy shown to have asymptotic logarithmic regret \cite{lai1985asymptotically} for distributions with bounded rewards. It basically assumes a frequenist perspective and estimates an empirical confidence bound for each arm based on the observations seen so far. Then it pulls the arm with the highest confidence bound.

\subsection{Gittins Index} 
Gittins index treats the bandit problem as an Markov Decision Process where each lever pull is taking a step along a Markov Chain. While, normally the cost of computing an optimal policy would be exponential in the number of K arms. The independence assumption between each arms allows us to decouple them and solve for a policy that models taking pulls along one arm or selecting a reference arm that represents selecting a different possible value. We computed the Gittins indices using the restart method proposed by Katehakis et al. \cite{katehakis1987multi}.

\begin{algorithm}
 \KwResult{Best Arm, $g^*$ }
 For Beta(1,1) prior: \\
\For{ t=1,2,...}{ 
 Draw $p_{j,t} \sim$ Beta($S_{j,t}+1$,$F_{j,t}+1$) for $j = 1,...,k$\\
 Play $I_t=j$ for $j$ with maximum $p_{j,t}$\\
 Observe reward $X_{I_t,t}$\\
 Update poster:\\
 Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
 Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\

 }
 \caption{Thompson Sampling}
\end{algorithm}

\section{Evaluating a Grasp on Gaussian Process Implicit Surface}
 In order to solve our problem definition, we must evaluate $P(Q(\Gamma)>0)$ for a given grasp plan $\Gamma$. We will first discuss how the GPIS is constructed, then which grasp metric $Q$ we chose and lastly proceed into evaluating $P(Q(\Gamma)>0)$ efficiently.

Here $\alpha_0$ and $\beta_0$ correspond to the intial shape parameters. To compute the above distribution we must draw samples from $p(S)$. In order to draw shape samples from a GPIS, one needs to sample from signed distance function, $sd$, over the joint on all points in the workspace $\mathcal{W}$ or $p(sd(\mathcal{W}))$. Since this is a GPIS, we know the following

@@

 To sample from $p(g)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$. Using Bayes rule we can rewrite this as

 \vspace{-2ex}
 \begin{align*}
 &p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))=\\
 &p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))p(c_i|\gamma_i(t),\mu(x),\Sigma(x))
 \end{align*}

 In section \ref{sec:contact}, we look at how to sample from $p(\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$. Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\mu(x),\Sigma(x))$ and present a novel visualization technique for the distribution on surface normals. Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution. 
 .
\subsection{Distribution on Contact Points}\label{sec:contact} 
We would like to find the distribution on contact point $\textbf{c}_i$. A contact point in terms of the GPIS and line of action model can be defined as the point, $t$, when the signed distance function is zero and no points before said point along the line have touched the surface. We express this as the following conditions:

\subsection{Distribution on Surface Normals}\label{sec:normals} 
Using Eq. \ref{eq:mean_gradient} and Eq. \ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively. Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$. We can now write

\vspace{-2ex}
\begin{align*}
p\big(\textbf{n}_i|\textbf{c}_i = \gamma(t)\big) = p\big(\textbf{n}_i |\mu(\gamma(t)), \Sigma(\gamma(t)) \big)
\end{align*}

>>>>

\author{Michael Laskey$^1$,Jeff Mahler$^1$, Zoe McCarthy$^1$,  Florian T. Pokorny$^3$, Sachin Patil$^1$,\\ Jur Van Den Berg$^4$,  Danica Kragic$^3$, Pieter Abbeel$^1$, Ken Goldberg$^2$% <-this % stops a space
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\small \{mdlaskey, zmccarthy, jmahler, sachinpatil, pabbeel\}@berkeley.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research and Department of Electrical Engineering and Computer Sciences; {\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley;  Berkeley, CA 94720, USA}%
\thanks{$^3$Computer Vision and Active Perception Lab, Centre for Autonomous Systems, School of Computer Science and Communication, KTH Royal Institute of Technology, Stockholm, Sweden {\small \{fpokorny, dani\}@kth.se}}%
\thanks{$^4$Google; Amphitheatre Parkway, Mountain View, CA 94043, USA {\small jurvandenberg@gmail.com}}%
}

@@

Consider a robot packing boxes in a shipping warehouse environment, where it may frequently encounter new consumer products and need to process them quickly.
The robot may need to rapidly plan grasps for these objects without prior knowledge of their shape, pose and even material properties like friction coefficient or center of mass.  Due to sensor noise and missing data due to partial visibility and object properties such as transparency, the robot may not be able to measure these quantities exactly.
Grasp planners that assume exact prior knowledge of object geometry or an exact measurement of pose may fail in this environment.

Grasp quality metrics have been developed to determine if a grasp will be successful or not and how much force it needs to exert to resist an opposing force, however most of them evaluate a grasp assuming all the parameters are known \cite{ferrari1992}.
This motivates using knowledge of uncertainty to select grasps, but most methods for evaluating the quality of a single grasp in the presence of uncertainty require use of an exhaustive sampling over the possible values of the uncertain quantity \cite{kim2012physically, weisz2012pose}.
To select a grasp with high quality this evaluation is often performed for a large set of potential grasps, which can be very time-consuming.
However, when evaluating a set of grasps we may be able to determine the difference of quality between grasps with only a few samples and throw away grasps that are likely to be suboptimal \cite{kehoe2012estimating}.
Thus, we can adaptively concentrate grasp quality evaluation on the grasps that are most likely to have the highest quality based on the evaluation done so far.

@@

Our main contribution in this paper is formulating the problem of planning grasps with a high expected quality in the presence of uncertainty as a budgeted multi-armed bandit model.
We use this formulation to rank a set of potential grasps by expected Ferrari-Canny quality \cite{ferrari1992} under shape uncertainty.
We use a budgeted multi-armed bandit model since we would like to execute only one grasp plan after evaluating the expected quality of many potential grasp plans.
We choose the model of uncertainty to be a Gaussian process implicit surface (GPIS), a Bayesian representation of shape uncertainty that seen recent use in various robotic applications~\cite{dragiev2011, hollinger2013}, however the method applies to any model of uncertainty that can be sampled.

We also show how to estimate distributions on the contact points and surface normals and center of mass using a GPIS shape representation. We then leverage these distributions to reduce the computational complexity of sampling from the GPIS model from $O(n^6)$ to $O(n^3)$, where the workspace is discretized as a $n \times n$ grid. Our experiments demonstrate that using the MAB sampling method improves the time to rank a set of 1000 grasps by 10x, an order of magnitude improvement, over the baseline Monte-Carlo approach. These promising results suggest that our MAB approach could be used on other types of uncertainty, such as pose, friction coefficent or center of mass and provide significant speed improvements.

@@

Currently, the most common method of evaluating the expected grasp quality under uncertainty is to rank a set of random grasps on an object using  samples on shapes, pose or parameters to evaluate a quality measure~\cite{christopoulos2007handling, kehoe2012estimating, kehoe2012toward}.
Monte-Carlo sampling involves drawing random samples from a distribution to approximate an expected value\cite{caflisch1998monte}, which can be slow when the distribution is high-dimensional, such as for distributions on possible shapes.
To address this, Kehoe et al.~\cite{kehoe2012estimating} demonstrated a procedure for finding a minimum bound on expected grasp quality given shape uncertainty, which reduced the number of terms needed in Monte-Carlo sampling in order to choose the highest quality grasps. The adaptive sampling pruned grasps using only the sample mean and did not utilize any estimates of how accurate the current sample mean is. 
Laaksonen et al.~\cite{laaksonen2012probabilistic} used Markov Chain Monte-Carlo (MCMC) sampling to estimate grasp quality and object pose  under shape and pose uncertainty.
MCMC simplified sampling from a complicated joint distribution on pose and shape, but it can be slow to converge to the correct distribution due to burn in and mixing conditions~\cite{andrieu2003introduction}.

@@

Traditional bandit algorithms minimize cumulative regret, which is the sum over each sub-optimal arm of the number of times that arm is pulled times the difference between the true expected reward of an optimal arm and the true expected reward of that sub-optimal arm. There are a number of algorithms for developing policies to balance exploration and exploitation.
One algorithm is $\epsilon-$greedy, which is the idea of choosing the arm with the highest empirical expected reward with $1-\epsilon$ probability and choosing a random arm with probability $\epsilon$ \cite{barto1998reinforcement}.
A class of algorithms that have stronger theoretical guarantees are from the Upper Confidence Bound (UCB) family.
UCB algorithms maintain the empirical expected reward based off of pulling each arm multiple times, while also estimating an upper bound on the true expected reward using assumptions on the probability distribution of rewards and number of times each arm has been sampled.

%In practice, when the distribution on the rewards of arms is not known, the empirical methods such as $\epsilon-$greedy have shown to have better performance in some situations \cite{kuleshov}.

Different to the normal bandit problem, we do not actually care about cumulative regret because the exploration and exploitation stage is decoupled from each other. For example in medical testing for patients it is important to always administer the best treatment for the given patient. However for the case of product testing in cosmetics it does not matter what products are administer in the testing phase, but only what final product is sold to the consumer. Thus, performance of Budgeted Multi-Armed Bandit models is measured in terms of the convergence of simple regret. Given a set of arms $\lbrace 1,...K \rbrace$ with respective mean rewards $\mu_1, ..., \mu_K$ and the optimal arm $\mu^* = \underset{k\in\lbrace 1, ..., K \rbrace}{\mbox{max}\mu_k}$. The regret at time $t$ is given by Eq. \ref{eq:simple_regret}, where $\mu_t$ is the estimate of the best arm at time $t$ from the previous observations.

\vspace{-2ex}
\begin{align}\label{eq:simple_regret}
r_t = \mu^* - \mu_t
\end{align}

Best arm identification has a wide variety of literature that largely falls into two camps: one where the algorithm terminates once a fixed confidence interval around the best arm is met and one where a set horizon is given and the algorithm has to choose a arm at that stopping time.

\subsection{Fixed Confidence}
In the fixed confidence setting the forecaster seeks to minimize the simple regret until a fixed confidence threshold is met at which point it terminates. Originally the problem was solved by racing algorithms, were methods used Hoeffding inequalities or the empirical Bernstein inequality to prune arms that were deemed not likely to succeed and used uniform allocation to explore the remaining set \cite{maron1993hoeffding} \cite{mnih2008empirical}. These methods were later extended to include not only the best arm, but return the top $m$ arms \cite{gabillon2012best}.

\subsection{Fixed Budget}
In the fixed budget setting the algorithm is given a stopping time and needs to return the best arm at that stopping time. Audibert el al. demonstrated an algorithm called Successive Rejects that given a budget divides up the time each arm is pull an can return the best arm with near-optimal probability depending on the hardness of the problem \cite{audibert2010best}. Other UCB like methods have been proposed as well that measure a confidence gap and then pull the arm with the highest confidence interval \cite{gabillon2012best}. In \cite{bubeck2009pure}, they showed a link between simple regret and cumulative regret that allowed for the analysis of the existing bandit algorithms like UCB1.

@@

\section{Bandit Algorithms For Best Arm Identification}\label{sec:algorithms}
\subsection{Thompson Sampling}
Thompson Sampling is a Bayesian method for the multi-armed bandit problem. The main idea behind it is to update the conjugate prior for the distribution of the arm recently pulled. Then sample from the prior distribution on all arms and pull the arm with the highest sample drawn. The full algorithm is shown in Algorithm 1.  Empirically this method has been shown to outperform frequentist methods like UCB \cite{chapelle2011empirical}

\begin{algorithm}
 \KwResult{Best Arm, $g^*$ }
 For Beta(1,1) prior: \\
\For{ t=1,2,...}{ 
 Draw $p_{j,t} \sim$ Beta($S_{j,t}+1$,$F_{j,t}+1$) for $j = 1,...,k$\\
 Play $I_t=j$ for $j$ with maximum $p_{j,t}$\\
 Observe reward $X_{I_t,t} \in \lbrace 0,1 \rbrace$\\
 Update posterior:\\
 Set $S_{I_t,t+1} = S_{I_t,t} + X_{I_t,t}$ \\
 Set $F_{I_t,t+1} = F_{I_t,t} + 1 - X_{I_t,t}$\\

 }
 \caption{Thompson Sampling for Beta-Bernoulli Process}
\end{algorithm}

\subsection{Upper Confidence Bound (UCB)}
The UCB strategy was the first strategy shown to have asymptotic logarithmic regret \cite{lai1985asymptotically} for distributions with bounded rewards. UCB estimates an empirical confidence bound for each arm based on the observations seen so far. Then it pulls the arm with the highest confidence bound. The confidence interval is derived from various concentration inequalities and assumes the reward function is bounded. The algorithm is in Algorithm 2 and assumes a Beta-Bernoulli Distribution, which is the case in our grasping.

\begin{algorithm}
 \KwResult{Best Arm, $g^*$ }
\For{ t=1,2,...}{ 
 Pick arm: $ k = \underset{k\in{1,...,K}}{\mbox{argmax}} \mu_k + \sqrt{\frac{6\mbox{log}(t)}{T_k}}$\\
 Observe reward $X_{k_t,t} \in \lbrace 0,1 \rbrace$\\
 Update\\
 $T_k= T_k +1$\\
 $\mu_k = \frac{T_k-1}{T_k}*\mu_k + \frac{1}{T_k}*X_{k,t}$\\
 }
 \caption{UCB for Beta-Bernoulli Process}
\end{algorithm}

\subsection{The Gittins Index Method} 
One possible solution to solve the MAB problem is to treat is as an Markov Decision Process (MDP) and use Markov Decision theory. This solution makes a lot of sense when the distribution is known because the all elements in the standard MDP tuple, $\lbrace S,A,T,R,\gamma \rbrace$, would be known and it is optimal with respect $\gamma$.

However, the \textit{curse of dimensionality} effects performance because if you have $K$ arms, a finite horizon of $T$ and a Beta-Bernoulli distribution on your arms then your state space is on the order of $T^{2*K}$. Hence the complexity of solving MAB using Markov Decision theory increases exponentially with the number of bandit processes. A key insight though was given by Gittins, who showed that instead of solving the $k$-dimensional MDP one can instead solve a $k$ 1-dimensional optimization problems: for each arm $i$, $i= 1,...,k$, and for each state of $x^i = \lbrace \alpha_0 +S_t, \beta_0 +F_t \rbrace^i$, where $S_t$ and $F_t$ correspond to the number of success and failures at pull $t$.

\vspace{-2ex}
\label{eq:git_indices}
\begin{align}
	v^i(x^i) = \underset{\tau>0}{\mbox{max}} \frac{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^tr^i(X_t^i)|X_0^i = x_i]}{\mathcal{E}[\sum_{t=0}^{\tau}\gamma^t|X_0^i = x_i]}
\end{align}

The indices can be considered as a computation of the value in choosing an arm conditioned on the fact that you will give up an choose another arm at some point. Once you know the state of your $k$ arms, the algorithm is to select the one with the highest index.  For Best Arm Identification you want your discount factor $\gamma$ to approach 1, since you should never stop pulling the best arm. We computed the Gittins indices offline using the restart method proposed by Katehakis et al. \cite{katehakis1987multi}.

\begin{algorithm}
 \KwResult{Best Arm, $g^*$ }
 For Beta(1,1) prior, Table of Indices $v$, Discount Factor $\gamma$: \\
\For{ t=1,2,...}{ 
 Pull arm $k = \underset{x_k \in X}{\mbox{argmax}} v(x_k)$\\
 Observe reward $R_{I_t,t} \in \lbrace 0,1 \rbrace$\\
 Update posterior:\\
 Set $S_{I_t,t+1} = S_{I_t,t} + R_{I_t,t}$ \\
 Set $F_{I_t,t+1} = F_{I_t,t} + 1 - R_{I_t,t}$\\
 Set $x_k = \lbrace 1 + S{I_t,t+1}, 1+F_{I_t,t+1} \rbrace$\\	
}
 \caption{The Gittins Index Method for Beta-Bernoulli Process}
\end{algorithm}

@@

The $L^1$ version of the metric works by taking as input the contact points $\textbf{c}_1,...,\textbf{c}_m \in \mathcal{R}^2$, surface normals $\textbf{n}_1,...,\textbf{n}_m \in \mathcal{R}^2$, center of mass $\textbf{z}$ and friction coefficient $\mu$. Then constructing a convex hull around the wrenches made up of those parameters and finding the radius of the largest unit ball centered at the origin in wrench space. A wrench is defined as concatenation of a force and torque vector.  If the convex hull does not enclose the origin, the grasp is not in force-closure. Formally, not being in force closure means there exists a wrench for which the grasp is not able to resist against, which occurs if the Quality metric $Q$ is less than zero. Thus a grasp can be parameterized by the following tuple $g = ( \textbf{c}_1,...,\textbf{c}_m,\textbf{n}_1,...,\textbf{n}_m,\mu, \textbf{z} )$.

Since we are in an uncertain environment, we are interested in calculating the probability of achieving force closure, or $P(Q>0)$, similar to  \cite{christopoulos2007handling}\cite{kehoe2012toward} . $P(Q>0)$ is computed by sampling from our distributions on pose, shape and material properties (friction coefficient and center of mass) and averaging the qualities that are computed. Reducing the time to find the best expected grasp from a set of a large number of grasps is the primary focus of the paper.

\subsection{Line of action}
In an uncertain environment one would not actually know the true $g$ because the actual grasp that is executed is non-deterministic. Thus, we have to work with the trajectory of the gripper. Similar to the work of \cite{christopoulos2007handling}, we assume that each gripper finger approaches along a \textit{line of action}, a 1D curve $\gamma(t)$ with endpoints $a$ and $b$ as seen in Fig. \ref{fig:line_of_action}.
A gripper finger starts at point $a$ and moves towards $b$, we assume $a$ is far enough away to be collision free of the object.
Each gripper contact is defined by a line of action, so we assume the following tuple is provided $\Gamma = ( \gamma_1(\cdot),...,\gamma_m(\cdot) )$, which designates a proposed \textit{grasp plan}.

\subsection{Types of Uncertainty}
In this work we consider the following types of uncertainty shape, pose, movement  and friction coefficient.  The property of force closure is not effected, by the location of center of mass because it only measures if a wrench can be resisted not how large the force is need to resist. Thus we calculate the expected The probabilistic relationship of all these types of uncertainty can be seen in Fig. \ref{fig:graphical_model}. We model each one of these with a corresponding distribution and demonstrate how MAB algorithms can handle all types of uncertainty.

\subsubsection{Distribution on Shape}

For shape we use a GPIS representation, which is explained in detail in Sec. \ref{sec:Appendix}. Essenttialy, a GPIS is a Gaussian distribution on a signed distance function that describes the workspace. The GPIS can be sampled from vian $N(\mu(x),\Sigma(x))$, where $\mu(x)$ and $\Sigma(x)$ are the mean and covariance functions of the GPIS. For our application we set $x$ to discretized points along each line of action $\gamma_i$ and for each sample see where the sample is equal to zero.  We will furthermore represent the $\mu(x)$ and $\Sigma(x)$ as the tuple $\theta = \rbrace\mu(x), \Sigma(x)\lbrace$.

\subsubsection{Distribution on Pose}
 \todo{Jeff can you write about Pose}

 \subsubsection{Distribution on Movement}
 In practice a robot may not be able to execute a desired
grasp plan $\Gamma$ exactly due to errors in trajectory following or
registration to the object \cite{kehoe2012estimating}. To handle this uncertainity, we sample the angle of approach $\rho$ of the proposed grasp plan $\Gamma$ from a zero mean one-dimensional Guassian $\rho \sim N(0,\sigma^2)$. In practice $\sigma^2$ can be set from repeatibility measurements for a robot \cite{mooring1986determination}.

 \subsubsection{Distribution on Friction Coefficient}
As shown in \cite{zheng2005}, uncertainty in friction coefficient can play a large role in grasp quality evaluation. The expected friction coefficient $E(\mu)$ can be derived by means of object classification and a look up table. However, because their could be material in between the objects surface and the robot gripper (i.e. dust, water, moisture). It is important to assume noise.  Thus, we purpose sampling the friction coefficient from a Gaussian around the expected friction coefficient $\mu \sim N(E(\mu),\sigma_{\mu}^2)$.

Thus to evaluate the $P(Q(\Gamma)>0)$, we sample from the graphical model shown in Fig. \ref{fig:graphical_model}. In the naive way sampling from the graphical model could be slow, however our goal is not to actually determine the probability of force closure but instead to determine the best grasp in a set $G$. Thus, our BMAB algorithms can efficiently sample from theses priors on the different types of uncertainty.

@@

@@

@@

Given a 2-D workspace $\mathcal{W}$, with an unknown object represented as a trained GPIS model, which we describe in Section \ref{sec:GP} and set of possible grasp plans $G$ which are generated either randomly or with a heuristic as in \cite{mahler2015gp}.
We are interested in determining Eq. \ref{eq:problem_def} with respect to a chosen grasp metric Q.

\vspace{-2ex}
\begin{align}\label{eq:problem_def}
\Gamma^* \in \underset{\Gamma \in G}{\mbox{argmax}} P(Q(\Gamma)>0)
\end{align}

@@

 To sample from $p(Q(\Gamma)>0)$, we need to sample from the distributions associated with a line of action $p(\textbf{n}_i,\textbf{c}_i|\gamma_i(t),\theta, \rho)$. Using Bayes rule and our graphical model we can rewrite this as

 \vspace{-2ex}
 \begin{align*}
 &p(\textbf{n}_i,\textbf{c}_i |\gamma_i(t),\theta,\rho)=\\
 &p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\theta,\rho)p(\textbf{c}_i|\gamma_i(t),\theta,\rho)
 \end{align*}

 In section \ref{sec:contact}, we look at how to sample from $p(\textbf{c}_i|\gamma_i(t),\mu(x),\Sigma(x))$ from a GPIS model. Then in section \ref{sec:normals}, we look at how to sample from $p(\textbf{n}_i|\textbf{c}_i,\gamma_i(t),\theta,\rho)$ and present a novel visualization technique for the distribution on surface normals. Lastly in section \ref{sec:mass}, we show a way to calculate the expected center of mass assuming a uniform mass distribution. 
 .
\subsection{Distribution on Surface Normals}\label{sec:normals} 
Using Eq. \ref{eq:mean_gradient} and Eq. \ref{eq:cov_gradient}, we can compute the mean of the gradient $ \mu_{\nabla}(x)$ and the covariance of the gradient $\Sigma_{\nabla}(x)$ respectively. Thus we can compute the distribution around the surface normal for a given point in $\mathcal{W}$. We can now write
